|

### 2021-10-16 appendix/appendix.Rmd
remove boldface table a8

\begin{table}[htp!]
\centering
\caption{Proportions for each bin used in the weighting process}
\label{tabweight}
\begin{tabular}{lccc}
\hline
& Sample & Population & Weighted \\
& Proportions & Proportions & Proportions \\
\hline
\textbf{Age less than 39}         & 0.50         & 0.34       & 0.34           \\
\textbf{Female}            & 0.18         & 0.12       & 0.12           \\
\textbf{Number of Seats = 9}            & 0.83         & 0.90       & 0.90           \\
\textbf{Number of Seats = 10}           & 0.10         & 0.06       & 0.06           \\
\textbf{Number of Seats = 11}           & 0.01         & 0.02       & 0.01           \\
\textbf{Number of Seats = 12}           & 0.01         & 0.01       & 0.01           \\
\textbf{Number of Seats = 13}           & 0.006        & 0.005      & 0.005          \\
\textbf{Number of Seats = 14}           & 0.01         & 0.004      & 0.005          \\
\textbf{Number of Seats = 15 or more}          & 0.02         & 0.009      & 0.008          \\
\textbf{Region = Central-West} & 0.11         & 0.08       & 0.08           \\
\textbf{Region = Northeast}     & 0.33         & 0.32       & 0.32           \\
\textbf{Region = North}        & 0.05         & 0.08       & 0.08           \\
\textbf{Region = Southeast}      & 0.30         & 0.30       & 0.30           \\
\textbf{Region = South}          & 0.20         & 0.21       & 0.21           \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[htp!]
\centering
\caption{Proportions for each bin used in the weighting process}
\label{tabweight}
\begin{tabular}{lccc}
\hline
& Sample & Population & Weighted \\
& Proportions & Proportions & Proportions \\
\hline
Age lower than 39         & 0.50         & 0.34       & 0.34           \\
Female            & 0.18         & 0.12       & 0.12           \\
Number of Seats = 9            & 0.83         & 0.90       & 0.90           \\
Number of Seats = 10           & 0.10         & 0.06       & 0.06           \\
Number of Seats = 11           & 0.01         & 0.02       & 0.01           \\
Number of Seats = 12           & 0.01         & 0.01       & 0.01           \\
Number of Seats = 13           & 0.006        & 0.005      & 0.005          \\
Number of Seats = 14           & 0.01         & 0.004      & 0.005          \\
Number of Seats = 15 or more          & 0.02         & 0.009      & 0.008          \\
Region = Central-West & 0.11         & 0.08       & 0.08           \\
Region = Northeast     & 0.33         & 0.32       & 0.32           \\
Region = North        & 0.05         & 0.08       & 0.08           \\
Region = Southeast      & 0.30         & 0.30       & 0.30           \\
Region = South          & 0.20         & 0.21       & 0.21           \\ \hline
\end{tabular}
\end{table}
